Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-18 providence/sections/pilot.tex
Update pilot.tex

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_sequence.png}
\caption{For each sample size from $1$ to $140$, the intermediate cumulative sum of ballots for the announced winner found in the sample is shown.}
\label{fig:pilot_sequence}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_sequence.png}
\caption{For each sample size from $1$ to $140$, the intermediate cumulative sum of ballots for the announced winner is shown, and the corresponding behavior is that of SO \BRAVO.}
\label{fig:pilot_sequence}
\end{figure}
